---
title: "Replication via R & Quarto - How Can Lower-Income Countries Collect More Taxes? The Role of Technology, Tax Agents, and Politics"
author: "Arunima Pandey"
date: "2024-10-28"
format: html
output: slidy_presentaion
---

# Presentation on Replication Project

## Introduction
This presentation replicates a key figure from the paper *"How Can Lower-Income Countries Collect More Taxes? The Role of Technology, Tax Agents, and Politics"* by Oyebola Okunogbe and Gabriel Tourek. The focus is on understanding the dataset used to generate insights and the specific challenges faced in replicating the results.

---

## Straight dive into the dataset
The dataset contains key metrics on tax revenues in Lagos State, Nigeria, and spans multiple years, which enables a comprehensive view of tax performance over time. The specific figure replicated in this presentation is Figure 4 from the paper, which visually represents "Lagos total tax from digest in billions" over the years.

---

## Challenges

### Loading .dta Files (Encoding and Conversion Errors)
- **Issue**: Encountered an error when loading `.dta` files: `unable to convert string to the requested encoding`. This error blocked some files from being read directly into R.

### Replicating the Graph with Complete Year Labels
- **Issue**: The axis labels initially did not display each year from 1999 to 2012, which made the plot less detailed and difficult to interpret.

### Error Messages: "Zero-length variable name" and Unexpected Symbols
- **Issue**: Errors such as `"Error: attempt to use zero-length variable name"` and `"Error: unexpected symbol"` were triggered by spaces in column names, like `Lagos total tax from digest in billions`.

### GitHub Pages Site Display Issue (404 Error)
- **Issue**: Received a 404 error when attempting to access the GitHub Pages site due to the absence of an `index.html` file in the repository's root directory.


```{r}
install.packages("knitr")
library(knitr)
```

```{r}
install.packages("quarto")
```

```{r}
install.packages("tinytex")
library(tinytex)
```

```{r}
if (!require(pacman)) install.packages("pacman")
pacman::p_load(knitr, rmarkdown, papaja)

```

```{r}
install.packages("haven")
library(haven)
```

```{r}
getwd()
```

```{r}
install.packages("ggplot2")
library(ggplot2)
```

```{r}
install.packages("dplyr")
library(dplyr)
```

```{r}
setwd("/Users/arunimapandey/dsarunima2024/Packagenew/Data/01_base/unuwider_data")
```

```{r}
data <- read_dta("/Users/arunimapandey/dsarunima2024/Packagenew/Data/01_base/unuwider_data/Figure1.dta", encoding = "latin1")
head(data)
```

```{r}
class(data)
```
```{r}

```

```{r}
colnames(data)
```

```{r}
summary(data)
```

```{r}
country_data <- data %>% select(country)
head(country_data)
```

```{r}
dataset <- read_dta("/Users/arunimapandey/dsarunima2024/Packagenew/Data/01_base/unuwider_data/figurex.dta")
head(dataset)
```

```{r}
install.packages("readxl")
library(readxl)
```

```{r}
set2 <- read_excel("/Users/arunimapandey/dsarunima2024/Packagenew/Data/01_base/lagos_data/Lagos.xlsx")
head(set2)
```

```{r}
colnames(set2)
```

```{r}
rownames(set2)
```




```{r}
names(set2)
```

```{r}
library(ggplot2)
install.packages("ggplot2")
library(ggplot2)
```

```{r}
ggplot(set2, aes(x = Year)) +
  geom_line(aes(y = `Lagos total tax from digest in billions`), color = "black") +
  labs(title = "Tax Revenues in Lagos State, Nigeria",
       x = "Year",
       y = "Lagos total tax from digest in billions")

```

```{r}
if (!require(pacman)) install.packages("pacman")
pacman::p_load(usethis)
create_github_token() 
```
```{r}
Sys.setenv(GITHUB_PAT = "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")  # Replace "your_token" with your actual GitHub token

```

